\input{letter_preamble}

I have been working as a full-stack developer since I graduated from the Systems Science program at
Gothenburg University, and have had the chance to try out different technologies and ways
of working. I believe the world of software development is so exciting because there is always something new
to learn and every colleague you meet have something interesting to share. I want to work where there is an
open and encouraging culture where new things can be tested and everyone feels welcome.

I like working as a full stack developer because I want to see the whole picture and I want to think of the work
I do as a complete solution that is handed over to the user of the product, but also because I am
excited about technology in general and think that it is super exciting to do both front-end and
back-end development. My strongest principles within software development that I follow in my daily work is:

\begin{itemize}
  \item Clean code
  \item Tested code
  \item Well separated modules
  \item Minimalism
\end{itemize}

I truly enjoy working together as a team, solving problems and making robust, well-tested and
performant software. I guess I am a typical developer in the sense that I really like
to dig down into details and write as efficient and well-structured code as I can. But I really do feel that coding
is teamwork and that you should always discuss and look for a second opinion regarding your solutions.
Both to make better results but also to learn.

Currently I am working in an agile team with a system that is built upon a containerized microservices architecture.
I develop new features as well as maintain and green keep the existing codebase.
The stack consists of .NET, Node.js, GraphQL and React.js.

Also I have a hobby-project that I have been working on during spare time that is available
on the Swedish iOS App Store. In this app I am using an open API from Västtrafik, Gothenburg’s public
transport provider, to build an app that is – in my opinion – a very useful complement to the
existing official app where you can subscribe and track your most commonly used stops and departures.
It is written in Swift and also includes a home-screen widget and an Apple Watch version. Find
the app by searching for “Nästa Resa” on the App Store.

Apart from software development I enjoy playing golf, following the Biathlon world cup,
hanging out with my wife, son and friends, solving Escape Rooms, running, finance and stocks,
 eating good food and reading the news. I see myself as a diplomatic
and easy going person who likes to have a good time as well as being serious about my work and
I feel very strongly for the tasks that I am involved in.

If you have any questions don’t hesitate to ask them. Looking forward to hearing from you!

Best regards,

Pontus Schuster Tengnäs
