{\itshape\Large\begin{center}
Experience
\end{center}}

\vspace{12px}

\begin{itemize}
  \item {\itshape Freelance Full-stack developer, Gothenburg 2022 – present}

  Freelancing as a Full-stack developer with a focus on app development. Currently in an assignment
  where I develop a Xamarin iOS/Android solution and a Golang backend.

  \item {\itshape Full-stack developer, Stena Line, Gothenburg 2020 – 2022}

  Working on a microservice solution consisting of services in .NET and Node.js with a React.js front-end.
  Using Typescript over Javascript and gRPC as primary communication protocol. Other technologies used are
  GraphQL and Docker.

  \item {\itshape Consultant, Evry Sweden, Gothenburg 2017 – 2020}

  Worked as a software developer consultant with a range of technologies and
  frameworks with a primary focus on front-end technologies but also backend development with Golang and .NET.
  Worked mostly with iOS, Android and Web development.

  \item {\itshape Consultant, Crepido AB, Mölndal 2016 – 2017}

  Worked as a software developer with a primary focus on mobile development with
  .NET and C\#. My work consisted of both front-end and back-end development.

  \item {\itshape Message Analyst, Enfo Zystems, Gothenburg 2015 – 2016}

  Part-time job during my studies. Supported software integrations by addressing
  different types of errors and problems in messages and infrastructure.

  \item {\itshape Java-supervisor, Gothenburg University, Gothenburg 2014 – 2015}

  Supervised and helped new students in Java-programming. Participated at specific
  occasions and explained concepts and principles within software development as
  well as answering to questions from the students.

  \item {\itshape Mailman, Posten Norge AS, Oslo 2011 – 2013}

  Worked as a mailman in Norway. Also participated in a project where we developed
  a smartphone app for employees at Posten Norge. My role in the project consisted
  of bringing up ideas and creating use-cases as well as testing the app in real life-scenarios.

  \item {\itshape Mailman, Posten Meddelande AB, Halmstad 2010 – 2011}

  Performed different types of tasks within the postal services.

\end{itemize}

\vspace{12px}

{\itshape\Large\begin{center}
Education
\end{center}}

\vspace{12px}

\begin{itemize}
  \item Gothenburg University, Gothenburg – Degree of Bachelor of Science with a major in Informatics. 2016.

  \item Sannarpsgymnasiet, Halmstad – Societal studies. 2007 – 2010.
\end{itemize}

\newpage

{\itshape\Large\begin{center}
Merits
\end{center}}

\vspace{12px}

{\itshape Nästa Resa; Private project}

https://itunes.apple.com/se/app/n\%C3\%A4sta-resa/id1356267708?mt=8

More apps that I have developed and worked on can be provided on request.\\

{\itshape Technical merits}

.NET, C\#, Golang, Javascript, Typescript, React.js, iOS, Android, Docker, Xamarin, GraphQL, HTML,
CSS, Microservice-architecture, Unit-testing, UI-testing, CI/CD, Swift, Node.js, SQL, MongoDb, REST, gRPC, Git.\\

{\itshape Methodologies}

Scrum, SAFe, Git flow, KanBan, Azure DevOps.\\

{\itshape Languages}

Swedish (native)

English (fluent, work-experience)

German (adequate, my wife is german)\\

{\itshape Other merits}

Swedish drivers license since 2009.\\

{\itshape Credentials}

Credentials and/or grades from Gothenburg University can be provided on request.\\

{\itshape Links}

GitHub: https://github.com/pontusntengnas

StackOverflow: https://stackoverflow.com/users/8639272/pontusnt

LinkedIn: https://www.linkedin.com/in/pontus-schuster-tengnas

Website: https://www.schustertengnas.com/
